\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/BadUSBC.tex
Update

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

>>>>

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  This obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  Ten volunteers participated. 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

### 2021-03-10 WOOT/Files/badusb.tex
Update

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
fact, during our experiment, no device had security notifications raised about
suspicious \ac{USB} devices and only mobile devices had raised a charging notification
about our \tool, which may not be a sufficient warning for users.

@@

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in the Figure\shuqing{fig 3 delete?}~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only does
the victim's device treat \tool as an external display, but also a valid \ac{HID}
input source. Hence we can achieve complete hijack of victim's device.

@@

This mode enables attacker to perform delicate operations that are beyond
automation. Moreover, this mode provides a backdoor that does not require a host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victims device
and provides a backdoor beyond detection of firewalls; however, this complete control
also comes with the price of high power consumption and risk of being detected
by the user.

>>>>

We build our threat model on the basic assumptions that common users without
technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications.

@@

\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can execute arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

@@

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only does
the victim's device treat \tool as an external display, but also a valid \ac{HID}
input source. Hence we can achieve complete hijack of the victim's device.

@@

This mode enables attackers to perform delicate operations that are beyond
automation. Moreover, this mode provides a backdoor that does not require a host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victim's device
and provides a backdoor beyond detection of firewalls; however, this complete control
also comes with the price of high power consumption and risk of being detected
by the user.

### 2021-03-10 WOOT/Files/experiment.tex
Update

\subsection{Attack Initialization}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen. For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option. However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications are raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (\nth{3} generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victims what mode should new screen be set to. \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a \ac{USB} Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
device in this experiment.  Besides disguising as normal \acp{HID} like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

Through this experiment, we have found that with video transmission and mouse
emulation, \tool extensively expanded the attack capability of BadUSB,
especially in mobile devices. In short, we have archived the complete hijack of the victim's
device in this experiment.

@@

We first introduce the technical background of our case study, sharing power
bank service and QR code payment.

\textbf{Sharing Power Bank}.  Sharing power banks provide users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank stations, charge their
device on the trip, return the rented power bank to the near stations, and pay
the rental fee.

@@

Not only do sharing power bank provide convenience to users, but it also
brings security issues.  We noticed that most of the power bank stations do not
check the integrity of power banks during the rental process, and users are
hardly cautious to check the power banks when connecting their devices.  An
attacker is able to tamper rented power banks and return them to a power bank
station causing a potential threat to subsequent users.

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  When the victim viewed text or photos withnt\shuqing{?} is typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
for micropayment purchases. For example, WeChat
Pay~\cite{Wechat-pay} regards transactions under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without needing permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like opportunistic theft of QR code but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

>>>>

\subsection{Attack Initialization}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen. For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option. However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victims what mode should the new screen be set to. \tool immediately injects a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a \ac{USB} Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker
successfully extracted text such as name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
device in this experiment.  Besides disguising as normal \acp{HID} like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After establishing the connection, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via the victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

Through this experiment, we have found that with video transmission and mouse
emulation, \tool extensively expanded the attack capability of BadUSB,
especially in mobile devices. In short, we have achieved the complete hijack of the victim's
device in this experiment.

@@

We first introduce the technical background of our case study, sharing power
banks and QR code payment.

\textbf{Sharing Power Banks}.  Sharing power banks provide users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank stations, charge their
device on the trip, return the rented power bank to the near stations, and pay
the rental fee.

@@

Sharing power banks not only provide convenience to users, but also bring security issues.  We noticed that most of the power bank stations do not
check the integrity of power banks during the rental process, and users are
hardly cautious to check the power banks when connecting their devices.  An
attacker is able to tamper rented power banks and return them to a power bank
station causing a potential threat to subsequent users.

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
====================================================
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  
When the victim viewed text or photos withnt is typically performed in the following steps:
====================================================
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
for micropayment purchases. For example, WeChat
Pay~\cite{Wechat-pay} regards transactions under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without needing permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like opportunistic theft of a payment code but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

### 2021-03-10 WOOT/Files/related_work.tex
Update

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is an example that abuses this standard and exfiltrate video data
from the victim without permission. However, in JFC, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, \ac{USB} inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous research~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,\shuqing{citation}
\cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
with the connected \ac{USB} devices as an RF transmitter and \cite{usbkiller,cable}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and invisibility is a
problem that cannot be ignored due to the spatial locality of radio frequency.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
it detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.

>>>>

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. However, in JFC, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, \ac{USB} inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous works~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and invisibility is a
problem that cannot be ignored due to the spatial locality of radio frequency.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.
